Output Summary

### 2022-01-26 03-post-process/compare-sim-to-obs.Rmd
Fix misc typos in Rmds

  breaks = c(0, 0.25, 0.5, 0.75, 0.9, 1.1, 1.25, 1.5, 1.75, 3)
  bin_names = levels(cut(runif(1e6, 0, 2), breaks = breaks, include.lowest = TRUE))
  names(cols) = c(bin_names[1:5], bin_names[5:9])
  bins = cut(x, breaks = breaks, include.lowest = TRUE)
  cols_use = cols[as.character(bins)]
  cols_use[is.na(cols_use)] = cols[5]
  alpha(unname(cols_use), 0.5)
}

>>>>

  breaks = c(0, 0.25, 0.5, 0.75, 0.9, 1.1, 1.25, 1.5, 1.75, 100)
  bin_names = levels(cut(runif(1e6, 0, 2), breaks = breaks, include.lowest = TRUE))
  names(cols) = c(bin_names[1:5], bin_names[5:9])
  bins = cut(x, breaks = breaks, include.lowest = TRUE)
  cols_use = cols[as.character(bins)]
  cols_use[is.na(cols_use)] = cols[5]
  alpha(unname(cols_use), 0.5)
}

### 2022-01-26 03-post-process/output-plots.Rmd
Fix misc typos in Rmds

```{r winter-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = observable, LH_type = i_spring, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
               main = pops[j])
}

@@

  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
}

@@

  if (j == 1) {
    legend("topright", legend = c("NOR", "HOR"), title = "Origin",
         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
  }
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
```

@@

  if (j == 1) {
    legend("topright", legend = c("NOR", "HOR"), title = "Origin",
         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
  }
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
```

@@

```{r lgr-to-ocean-bxp}
par(mfrow = c(1,3))
my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("rho_Lphi_Ma_O0[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
```

@@

```{r bon-to-lgr-bxp}
par(mfrow = c(1,3))
my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = c("NOR", "HOR"))
my_boxplot(sub_index("rho_Lphi_Rb_Ra[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
```

@@

```{r rho_plot, fig.width = 6, fig.height = 8}
# get the names of all rho parameters
# these are elements of a correlation matrix
# but because the rho term is the same for all population pairs, it is sufficient 
# to summarize just one element from each matrix
rho_params = c(
  match_params(post, "rho_.+[2,1]"),
  match_params(post, "rho_.+[2,1,1]"),
  match_params(post, "rho_.+[2,1,2]")
)

@@

# make prettier names for each term
rho_names = c(
  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
  "rho_Lpi[2,1]" = "Mig. Stategy Apportionment",
  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
  )
rho_summs$name = rho_names[rho_summs$param]

>>>>

```{r winter-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = ts_yrs, LH_type = i_spring, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
               main = pops[j],
               yrs = all_yrs[ts_yrs])
}

@@

  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,1,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,2,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,3,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,4,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,5,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  plot_tseries(post_summ(post, sub_index("^p_Sa_prime[year,6,pop]$", pop = j, year = ts_yrs)), get_obs_ests_multinomial(jags_data$x_Sa_prime[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"), yrs = all_yrs[ts_yrs])
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Carcasses")
}

@@

  if (j == 1) {
    legend("topright", legend = origins, title = "Origin",
         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
  }
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
```

@@

  if (j == 1) {
    legend("topright", legend = origins, title = "Origin",
         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
  }
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
```

@@

```{r lgr-to-ocean-bxp}
par(mfrow = c(1,3))
my_boxplot(sub_index("mu_phi_Ma_O0[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
my_boxplot(sub_index("sig_Lphi_Ma_O0[origin]", origin = "."), "Process SD", ylim = c(0,1), ticklab = origins)
my_boxplot(sub_index("rho_Lphi_Ma_O0[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
```

@@

```{r bon-to-lgr-bxp}
par(mfrow = c(1,3))
my_boxplot(sub_index("mu_phi_Rb_Ra[origin]", origin = "."), "Average Migration Survival", ylim = c(0,1), ticklab = origins)
my_boxplot(sub_index("sig_Lphi_Rb_Ra[origin]", origin = "."), "Process SD", ticklab = origins)
my_boxplot(sub_index("rho_Lphi_Rb_Ra[2,1]"), "Among-origin Correlation", ylim = c(-1,1), ticklab = c(""))
```

@@

```{r rho_plot, fig.width = 6, fig.height = 7}
# get the names of all rho parameters
# these are elements of a correlation matrix
# but because the rho term is the same for all population pairs, it is sufficient 
# to summarize just one element from each matrix
rho_params = c(
  match_params(post, "rho_.+[2,1]"),
  match_params(post, "rho_.+[2,1,1]"),
  match_params(post, "rho_.+[2,1,2]")
)

@@

# make prettier names for each term
rho_names = c(
  "rho_Lphi_E_Pb[2,1]" = "Egg-to-Parr Survival",
  "rho_Lpi[2,1]" = "Mig. Strategy Apportionment",
  "rho_Lphi_Ma_O0[2,1]" = "LGR to Ocean Survival",
  "rho_Lphi_O0_O1[2,1]" = "Yr1 Ocean Survival",
  "rho_Lphi_Rb_Ra[2,1]" = "BON to LGR Survival",
  "rho_Lphi_Sb_Sa[2,1]" = "Pre-spawn Survival",
  "rho_Lphi_Pa_Mb[2,1,1]" = "Overwinter Survival (Fall)",
  "rho_Lphi_Pa_Mb[2,1,2]" = "Overwinter Survival (Spring)",
  "rho_Lphi_Mb_Ma[2,1,1]" = "Trib to LGR Survival (NOR)",
  "rho_Lphi_Mb_Ma[2,1,2]" = "Trib to LGR Survival (HOR)",
  "rho_Lpsi_O1[2,1,1]" = "Age-3 Maturation (NOR)",
  "rho_Lpsi_O1[2,1,2]" = "Age-3 Maturation (HOR)",
  "rho_Lpsi_O2[2,1,1]" = "Age-4 Maturation (NOR)",
  "rho_Lpsi_O2[2,1,2]" = "Age-4 Maturation (HOR)"
  )
rho_summs$name = rho_names[rho_summs$param]
